A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2020-07-23 07_Manuscript.Rmd
Edit introductory paragraph and add new references on MB history in Oz

Mungbean [*Vigna radiata* (L.) Wilczek] is a pulse crop primarily grown in south-east Asia for human consumption as an affordable source of protein [@Lambrides2007].
The bean pod or grain can be consumed raw or added to meals after sprouting.
The dried grain can also be ground into a protein enriched flour for uses such as noodles, biscuits and cakes [@Chankaew2013].

Mungbean was first brought to Australia in the 1930s for use as a forage or green manure crop and it was only as recent as the 1960s until that mungbean was grown commercially [@aboutAMA, @Chauhan2018].
At the end of the 1980s between 3 - 10 thousand hectares were being harvested for dried beans, of which mungbean is categorised by the FAO statistics data repository [@FAOSTAT].
In the decade leading up to 2018 between 35 - 86.4 thousand hectares of dried beans were planted annually. 
This increase is attributed high value export markets and to the improved yields in the new cultivars [@Clarry2016].
Currently mungbean is predominantly grown in southern Queensland and northern New South Wales as a short season summer legume crop.
In 2019, approximately 90&nbsp;% of Australian mungbean was grown for export with lucrative returns of up to \$1300&nbsp;AU a tonne [@QueenslandGovernment2019].
Mungbean potentially yields up to 3 tonnes per hectare [@ThomasRobert2004], but due to high variability in yields between seasons and locations, the average Australian farm still yields less than 1 tonne per hectare [@Chauhan2018].

>>>>

Mungbean [*Vigna radiata* (L.) Wilczek] is a pulse crop primarily grown in south-east Asia for human consumption as an affordable source of protein [@Lambrides2007].
The bean pod or grain can be consumed raw or added to meals after sprouting.
The dried grain can also be ground into a protein enriched flour for uses in noodles, biscuits and cakes [@Chankaew2013].

Mungbean was first brought to Australia in the 1930s for use as a forage or green manure crop.
However, it was only somewhat recently, the 1960s that mungbean was grown commercially [@Lawn1978; @Chauhan2018].
Prior to the 1970s the total area grown in Australia rarely exceeded 1000 hectares [@Lawn1978].
At the end of the 1980s, between 3,000 to 10,0000 hectares were being harvested for dried beans in Australia, of which mungbean is categorised by the FAO statistics data repository [@FAOSTAT].
In the decade leading up to 2018 between 35 - 86.4 thousand hectares of dried beans were planted annually.
This increase is attributed high value export markets and to the improved yields in the new cultivars [@Clarry2016].
Currently mungbean is predominantly grown in southern Queensland and northern New South Wales as a short season summer legume crop.
In 2019, approximately 90&nbsp;% of Australian mungbean was grown for export with lucrative returns of up to \$1300&nbsp;AU a tonne [@QueenslandGovernment2019].
Mungbean potentially yields up to 3 tonnes per hectare [@ThomasRobert2004], but due to high variability in yields between seasons and locations, the average Australian farm still yields less than 1 tonne per hectare [@Chauhan2018].
